% CREATED BY DAVID FRISK, 2016
\begin{thebibliography}{69}
\bibitem{CPGHauert}
Sabine Hauert. \textit{Bio-mimetic
Robot Control}, Lectures in Bio-Inspired Artificial Intelligence at University of Bristol, February 16, 2016

\bibitem{GAHauert}
Sabine Hauert. \textit{Artificial Evolution}, Lectures in Bio-Inspired Artificial Intelligence at University of Bristol, February 9, 2016

\bibitem{CPGmodels}
G. M. Shephard. \textit{Neurobiology, 3rd ed. 1994, ch. 20, pp. 435–451.}

\bibitem{matsuoka}
K. Matsuoka. \textit{Mechanisms of frequency and pattern control in the neural rhythm generators}. Biol Cybern, vol. 47, no. 2–3, pp. 345– 353, 1987.

\bibitem{CPGequations}
G. Taga, Y. Yamaguchi, and H. Shimizu. \textit{Self-organized control of bipedal locomotion by neural oscillators in unpredictable environ- ment}, Biological Cybernetics, vol. 65, pp. 147–159, 1991.

\bibitem{wahde}
Mattias Wahde. \textit{Biologically Inspired Optimization Methods: An Introduction}. WIT Press, 2008.

\bibitem{liu}
Guang Lei Liu, Maki K. Habib, Keigo Watnabe, and Kiyotaka Izumi. \textit{Central pattern generators based on matsuoka oscillators for the locomotion of biped robots}. Artif Life Robotics, 12:264–269, 2008.

\bibitem{shan}
Jiang Shan, Cheng Junshi, and Chen Jiapin. \textit{Design of central pattern generator for humanoid robot walking based on multi-objective ga}. In Proceedings of the 2000 IEEE/RSJ International Conference on Intelligent Robots and Systems, volume 3, pages 1930–1935. IEEE.

\bibitem{CPGwolff}
Krister Wolff, Jimmy Pettersson, Almir Heralic, and Mattias Wahde. \textit{Structural Evolution of Central Pattern Generators for Bipedal Walking in 3D Simulation}, October 11, 2006

\bibitem{bioloidMan}
Robotis Inc. \textit{Bioloid Premium Kit Assembly Manual}, \url{http://www.robotis.com/download/doc/BIO_PRM_Humanoid_ASM.pdf}, Accessed 30/10/2017

\bibitem{studentProj}
Helga Kristín Ólafsdóttir et al. \textit{Evolving a human-like gait}, \url{https://drive.google.com/file/d/0By4BzP3-lonJTnJTdmdGSVpJVDg/view}, Accessed 30/10/2017

\bibitem{bioloid}
Trossen Robotics. \textit{Bioloid Premium Robot Kit}, \url{http://www.trossenrobotics.com/p/bioloid-premium-robot-kit.aspx}, Accessed 30/10/2017

\bibitem{sensorfusion}
Fredrik Gustafsson. \textit{Sensor fusion}, Linköping University, \url{https://play.google.com/store/apps/details?id=com.hiq.sensor&hl=en}, Accessed 31/10/2017
\bibitem{v-rep}
Coppelia Robotics, \textit{V-REP Virtual Robot Experimentation Platform}, \url{http://www.coppeliarobotics.com/}, Accessed 31/10/2017
\bibitem{dongle}
Trossen Robotics. \textit{Robotis USB2Dynamixel Adapter}, \url{http://www.trossenrobotics.com/robotis-bioloid-usb2dynamixel.aspx}, Accessed 31/10/2017
\end{thebibliography}
